\section{Bj\"ork's approach to existence of b-functions}

\begin{theorem}[Bj\"ork]\label{Theorem 8.4}
    Let $M$ be a holonomic $\mathcal{D}_X$-module with a good filtration $\Omega_{\bullet} M$ over $V_{\bullet} \mathcal{D}_X$. There exists $b(s) \in \mathbb{C}[s]$ such that
    \[
        b(t\partial_t - k) \text{ kills } \frac{\Omega_k M}{\Omega_{k-1} M}, \quad \forall k \in \mathbb{Z}.
    \]
    The monic minimal degree $b(s)$ is called the $\textbf{$b$-function}$ of $M$ along $Y$.
\end{theorem}
\begin{lemma}\label{lemma 8.5}
    Let $Y$ be a smooth variety over $\mathbb{C}$, $N$ a holonomic $\mathcal{D}_Y$-module, and $\theta\in \mathrm{End}_{\mathcal{D}_Y}(N)$. Then there exists $b(s)\in\mathbb{C}[s]$ such that $b(\theta)=0$.
\end{lemma}
\begin{proof}
    Since $N$ is holonomic, we obtain that
    \[
        \mathrm{Ch}(N) = \bigcup_{i} T^*_{Y_i} Y,
    \]
    with $Y_{i}$ locally closed.

    Take a $Y_i$ of maximal dimension and take an open subset $U \subset Y$ such that $Y_{i}^{\circ} \hookrightarrow U$ is a closed embedding with $\overline{Y_i^{\circ}} = Y_{i}$ and $U \cap (\bigcup_{j\neq i}Y_j) = \varnothing$. Then
    \[
        \mathrm{Ch}(N|_U) = T^*_{Y_i^\circ} U,
    \]
    which implies by Kashiwara's equivalence (Theorem \ref{thm:kashiwara_equiv} and Corollary \ref{cor:kashiwara_equiv_conormal}) that
    \[
        N|_U = \mathcal{O}_{Y_i^\circ} \otimes L[\partial_1, \ldots, \partial_k]
    \]
    with $L$ a local system on $Y_i^\circ$ (which corresponds to an integrable connection).

    We have $\mathrm{End}(N|_U) = \mathrm{End}_{\mathbb{C}}(L)$. Therefore, there exists $b_i(s) \in \mathbb{C}[s]$ such that $b_i(\theta|_{U}) = 0$.

    Now, take $N_1 = b_1(\theta)N$. Then
    \[
        \mathrm{Ch}(N_1) = \bigcup_{j \neq i} T^*_{Y_j} X.
    \]
    We are done by induction.
\end{proof}

\begin{lemma}[Lemma 20.2]
    Let $Y$ be a smooth variety over $\C$, $N$ a holonomic $D_Y$-module, and
    $\theta \in \End_{D_Y}(N)$. Then there exists a nonzero polynomial
    $b(s)\in \C[s]$ such that $b(\theta)=0$ in $\End_{D_Y}(N)$.
\end{lemma}

\begin{proof}
    We argue by induction on the length $\ell(N)$ in the abelian category of holonomic
    $D_Y$-modules. Such a length is finite by \cite[Prop.\ 6.37]{mustata2023dmodules}.
    If $N=0$ there is nothing to prove.

    \medskip
    \noindent\textbf{Step 1: Reduction to finding a non-injectivity point.}
    Let $u:=\theta$. If we can find $\lambda\in \C$ and a point $y\in Y$ such that the
    stalk map $(u-\lambda\Id)_{y}:N_y\to N_y$ is not injective, then
    $N_1:=\ker(u-\lambda\Id)\subset N$ is a nonzero holonomic submodule, stable under $u$.
    By induction we can find nonzero $p_1,p_2\in \C[s]$ with $p_1(u|_{N_1})=0$ and
    $p_2(u|_{N/N_1})=0$, hence $p(u)=0$ on $N$ for $p=p_1p_2$.

    Thus it suffices to produce such a $\lambda$ and $y$.

    \medskip
    \noindent\textbf{Step 2: Replace $Y$ by the support and shrink to the locus where $N$ is a bundle.}
    After replacing $Y$ by a nonempty open subset (which does not affect the existence of
    a point where $u-\lambda\Id$ fails to be injective), we may assume $\Supp(N)$ is a
    smooth irreducible subvariety of $Y$. By Kashiwara's equivalence, if
    $i:\Supp(N)\hookrightarrow Y$ is the inclusion, then $i_+$ induces an equivalence between
    $D_{\Supp(N)}$-modules and $D_Y$-modules supported on $\Supp(N)$, so we may replace
    $Y$ by $\Supp(N)$ and assume $\Supp(N)=Y$ \cite[Thm.\ 6.20]{mustata2023dmodules}.

    Since $N$ is holonomic, after shrinking $Y$ further we may assume that $N$ is
    $\cO_Y$-coherent (hence locally free) on this open set \cite[Rem.\ 6.30]{mustata2023dmodules};
    moreover $\cO_Y$-coherent left $D_Y$-modules are locally free \cite[Prop.\ 3.18]{mustata2023dmodules}.
    Therefore on this open set, $N$ is a vector bundle with an integrable connection
    (the $D_Y$-action is equivalent to a flat connection) \cite[Prop.\ 3.10]{mustata2023dmodules}.

    \medskip
    \noindent\textbf{Step 3: Finite-dimensionality of $\End_{D_Y}(N)$ via analytification and a local system.}
    Let $E:=\End_{\cO_Y}(N)$.
    The $D_Y$-module structure on $N$ induces an integrable connection on $E$, and
    \[
        \End_{D_Y}(N)\;=\;\Gamma(Y,E^\nabla),
    \]
    where $E^\nabla\subset E$ is the subsheaf of horizontal sections.
    After analytification, the horizontal sections $(E^{an})^\nabla$ form a local system
    on $Y^{an}$, by the classical Riemann--Hilbert correspondence
    (local systems $\leftrightarrow$ flat bundles) \cite[Thm.\ 7.5]{mustata2023dmodules}.
    Since $Y^{an}$ is connected, the natural evaluation map
    $\Gamma(Y^{an},(E^{an})^\nabla)\to (E^{an})^\nabla_y$ is injective for every $y$,
    hence $\Gamma(Y^{an},(E^{an})^\nabla)$ is finite-dimensional.
    This implies $\dim_\C \End_{D_Y}(N)<\infty$ on our chosen open set.

    Consequently $u$ satisfies a nonzero polynomial relation on that open set: take the
    minimal polynomial $p(s)$ of $u$ as an element of the finite-dimensional $\C$-algebra
    $\End_{D_Y}(N)$ on the open set, so $p(u)=0$ there.

    Write $p(s)=\prod_{i=1}^r (s-\lambda_i)$ over $\C$.
    If all $(u-\lambda_i\Id)$ were injective on every stalk, then their product $p(u)$
    would be injective on every stalk, contradicting $p(u)=0$ and $N\neq 0$.
    Hence there exist $i$ and a point $y$ such that $(u-\lambda_i\Id)_y$ is not injective.

    By Step~1, this yields a nonzero polynomial $b(s)$ with $b(u)=0$ on $N$, i.e. $b(\theta)=0$.
\end{proof}

\begin{remark}[{How to read $\cO\otimes L[\partial]$}]
    In purely algebraic terms, Kashiwara's equivalence gives $N|_U \simeq i_+(M)$ for a
    $D_{Y_i^\circ}$-module $M$ on the smooth closed subvariety $i:Y_i^\circ\hookrightarrow U$.
    In local coordinates where $Y_i^\circ$ is cut out by one equation $z=0$, one has
    the \emph{algebraic} local model
    \[
        i_+(M)\;\cong\; M\otimes_\C \C[\partial_z],
    \]
    with explicit $D_U$-action (in particular $z$ acts nilpotently and $\partial_z$ acts
    by shifting the $\partial_z$-power) \cite[Thm.\ 6.20, proof]{mustata2023dmodules}.
    If moreover $M$ is $\cO$-coherent, then $M$ is a vector bundle with flat connection,
    and after analytification $M^{an}\simeq \cO^{an}\otimes_\C L$ for a local system $L$
    \cite[Thm.\ 7.5]{mustata2023dmodules}. This explains the heuristic notation
    $\cO_{Y_i^\circ}\otimes L[\partial]$ used in some notes: it is the analytification of
    the algebraic formula above.
\end{remark}




\begin{theorem}\label{Theorem 8.6}
    Let $M$ be a finitely generated $\mathcal{D}_{X}$-module, and $\Omega_{\bullet}M$ a good filtration over $V_{\bullet}\mathcal{D}_{X}$. Then $j(\mathrm{gr}_{\bullet}^\Omega M)\ge j(M)$.
\end{theorem}
\begin{proof}
    If $\mathrm{gr}^\Omega_{\bullet}M=0$, there is nothing to prove, so we assume $\mathrm{gr}^\Omega_{\bullet}M\neq 0$ and $\ell=j(\mathrm{gr}_{\bullet}^{\Omega}M)<j(M)$.

    Then the $E_1$-page of the spectral sequence that converges to $\mathrm{Ext}_{\mathcal{D}_{X}}^{j}(M,\mathcal{D}_{X})$ satisfies:
    \[
        0 \rightarrow \operatorname{Ext}^{\ell}(\operatorname{gr}_{\bullet}^{\Omega} M, \operatorname{gr}^{V}_{\bullet}\mathcal{D}_X)
        \xrightarrow{d_1}
        \operatorname{Ext}^{\ell+1}(\operatorname{gr}_{\bullet}^{\Omega} M, \operatorname{gr}^{V}_{\bullet}\mathcal{D}_X).
    \]
    So we obtain that $E^{\ell}_{\bullet}(2)=\ker d_{1}\subseteq\operatorname{Ext}^{\ell}(\operatorname{gr}_{\bullet}^{\Omega} M, \operatorname{gr}^{V}_{\bullet}\mathcal{D}_X)$ since no images map to $E^{\ell}_{\bullet}(1)$.

    Then we have the following exact sequence with the quotient $N=E^{\ell}_{\bullet}(1) /\ker d_{1}\simeq d_{1}(E_{\bullet}^{\ell}(1))\subseteq E^{\ell+1}_{\bullet}(1)$:
    \[
        0 \rightarrow E_{\bullet}^{\ell}(2) \rightarrow \operatorname{Ext}^{\ell}(\operatorname{gr}_{\bullet}^{\Omega} M, \operatorname{gr}^{V}_{\bullet}\mathcal{D}_X)
        \rightarrow N \rightarrow 0.
    \]
    With $\mathrm{gr}_{\bullet}^V\mathcal{D}_{X}$ Auslander regular, we obtain that for $N\subseteq \mathrm{Ext}^{\ell+1}(\operatorname{gr}_{\bullet}^{\Omega} M, \operatorname{gr}^{V}_{\bullet}\mathcal{D}_X)$, $j(N)\ge \ell+1$.

    Since $j(M)>\ell$, we have $E_{\bullet}^{\ell}(r) = \operatorname{gr}_{\bullet} \operatorname{Ext}^{\ell}(M, \mathcal{D}_X) = 0$ for some $r\gg 0$, and $E^{\ell}_{\bullet}(r)=\ker d_{r}$.

    Also $\mathrm{gr}_{\bullet}^V\mathcal{D}_{X}$ is a noetherian ring, so we have
    \[
        j(\operatorname{Ext}^{\ell}(\operatorname{gr}_{\bullet}^{\Omega} M, \operatorname{gr}^{V}_{\bullet}\mathcal{D}_X) )\ge\ell+1,
    \]
    which is a contradiction.
\end{proof}


\begin{proof}[proof of (\ref{Theorem 8.4})]
    \quad

    By Theorem \ref{Theorem 8.6}, $j(\mathrm{gr}_{\bullet}^\Omega M)\ge j(M)=n$. If $\mathrm{gr}_{\bullet}^\Omega M=0$, take $b(s)=0$. If not, then $\mathrm{dim\ ch}(\mathrm{gr}^\Omega_{\bullet}M)\ge n$.

    Since $\mathrm{gr}_{\bullet}^V\mathcal{D}_{X}$ is a Auslander regular ring, we obtain that $j(\mathrm{gr}_{\bullet}^\Omega M)+\mathrm{dim}(\mathrm{Ch}(\mathrm{gr}_{\bullet}^\Omega M))=2n=2\mathrm{dim}T_{Y}X$, then $\mathrm{gr}^\Omega_{\bullet} M$ is holonomic over $T_Y X$.

    Now, take $\theta=\bigoplus \limits_{i}(t\partial_{t}-i),$ then $\theta\in\mathrm{End}_{\mathcal{D}_{T_{Y}X}}(\mathrm{gr}_{\bullet}^\Omega M)$. By Lemma \ref{lemma 8.5}, there exists $b(s)\in\mathbb{C}[s]$ s.t. $b(\theta)=0$, In particular, $b(t\partial_{t}-k)$ kills $\frac{\Omega_{k}M}{\Omega_{k-1}M}$ for all $k$.
\end{proof}

\begin{remark}
    It is poosible that $\mathrm{gr}_{\bullet}^\Omega M=0$. In fact, take $M=\mathbb{C}[t, \frac{1}{t}]e^{\frac{1}{t}}=\mathcal{D}_{X}\cdot e^{\frac{1}{t}}$, take $\Omega_{k}M=V_{k}\mathcal{D}_{X}\cdot e^{\frac{1}{t}}$, which is a good filtration. Since $t\partial_{t}e^{\frac{1}{t}}= -\frac{1}{t} e^{\frac{1}{t}}$, we have $\Omega_{k}M=M$ and $b(s)=1$.
\end{remark}

\begin{theorem}[Kashiwara-Malgrange]\label{Theorem 8.7}
    Let $M$ be a holonomic $\mathcal{D}_{X}$-module, there exists unique good filtration $V_{\bullet}M$ and $b(s)\in\mathbb{C}[s]$ s.t.
    \begin{enumerate}
        \item $\mathrm{Re}(\text{roots of }b(s))\subseteq(-1,0]$;
        \item $b(t\partial_{t}-k)$ kills $\frac{V_{k}M}{V_{k-1}M}$.
    \end{enumerate}
    And the filtration is called $V$-filtration.
\end{theorem}
\begin{proof}
    This is Kashiwara's trick:
    Set $\Gamma_{n}=\Omega_{n+k}$, we then have $b(t\partial_{t}-n-k)$ kill $\Gamma_{n} /\Gamma_{n-1}$ for all $n$, thus taking $k\gg 0$, we can assume $\mathrm{Re}(\text{roots of }b(s))>0$.

    Let $b(s)=(s-\alpha)^\ell b_{1}(s)$ s.t. $(s-\alpha)\nmid b_{1}(s)$; set $\Gamma_{n}'=\Gamma_{n-1}+(t\partial_{t}-\alpha-n)\Gamma_{n}$, then $(t\partial_{t}-(\alpha-1)-n)^\ell b_{1}(t\partial_{t}-n)$ kills $\frac{\Gamma_{n}'}{\Gamma_{n-1}'}$ for all $n$.

    If $\mathrm{Re}(\alpha-1)\notin(-1,0]$, repeat this until all roots moved in $(-1,0]$.
\end{proof}

\begin{definition}
    \quad

    \begin{enumerate}
        \item  $M$ is called $Q\textbf{-specializable}$ along $Y$ if the $b$-function has all its roots in $Q$, where $Q \subset \mathbb{C}$ is a subfield.
        \item If $M$ is $Q$-specializable, then for all $\beta \in Q$, take $k = \lceil \beta \rceil$, then define $$V_{\beta} M = \pi^{-1} \left( \bigoplus_{\alpha \leq \beta} \left( \frac{V_k M}{V_{k-1} M} \right)^{\alpha} \right),$$and $$V_{<\beta} M = \pi^{-1} \left( \bigoplus_{\alpha < \beta} \left( \frac{V_k M}{V_{k-1} M} \right)^{\alpha} \right),$$where $\left( \frac{V_k M}{V_{k-1} M} \right)^{\alpha}$ is the $\alpha$-eigenspace of $\frac{V_k M}{V_{k-1} M}$ w.r.t. the $t\partial_t$-action, and $\pi: V_k M \rightarrow \frac{V_k M}{V_{k-1} M}$; then we get a $\mathbb{Q}$-indexed $V$-filtration s.t.  $$\mathrm{gr}_{\alpha}^{V} M = \frac{V^{\alpha} M}{V^{<\alpha} M} = \left( \frac{V_k M}{V_{k-1} M} \right)^{\alpha}$$ with $t\partial_t - \alpha$ acts on $\mathrm{gr}_{\alpha}^{V} M$ nilpotently.
    \end{enumerate}
\end{definition}
\begin{example}
    Let $X=\mathbb{A}^{1}_{\mathbb{C}}$ and $M = \mathbb{C}\left[ t, \frac{1}{t} \right]e^{\frac{1}{t}}$ an irregular holonomic $\mathcal{D}$-mod.

    Consider $V$-filtration along $t = 0$. The $V$-filtration on $M$ exists by Theorem \ref{Theorem 8.7}$$\partial_t e^{\frac{1}{t}} = -\frac{1}{t^2} e^{\frac{1}{t}}\text{ which implies that }t\partial_t e^{\frac{1}{t}} = -\frac{1}{t} e^{\frac{1}{t}}(\ast)$$Take $\Omega_i M = V_i \mathcal{D}_{X} \cdot e^{\frac{1}{t}}$ for $i \in \mathbb{Z}$, then $\Omega_0 M = M$ for $(\ast)$ holds, further, we obtain that $\Omega_1 M = t \Omega_0 M = t M = M$ and $\Omega_i M = M$ for all $i\in \mathbb{Z}$. Finally, we find out that $\Omega_{i}M$ is the $V$-filtration we want with the $b$-function of $M$ is $1$.

\end{example}

\begin{theorem}
    If M is a regular holonomic $\mathcal{D}_X$-mod, then its V-filtration is not trivial. In particular, its b-function is not $1$.
\end{theorem}

\begin{proof}[Sketch of proof]
    First, each $V_i M$ is a $V_0 \mathcal{D}_X$-module and $V_0 \mathcal{D}_X = \mathcal{D}_X^{\log}$ w.r.t. $(t = 0)$. Since $V_i M$ has no $t$-torsion for all $i < 0$, $\mathrm{Ch}(V_i M)$ has no component over $(t = 0)$, for all $i < 0$.

    Further, we obtain that $\mathrm{Ch}^{\log}\left(\frac{V_i M}{V_{i-1} M}\right) = \mathrm{Ch}^{\log}\left(\frac{V_i M}{t V_i M}\right)= \mathrm{Ch}^{\log}(V_i M)\big|_{(t=0)}$, thus $\frac{V_i M}{V_{i-1} M} \neq 0.$

\end{proof}


\begin{example}\label{Example 8.11}

    Let $X = \mathbb{A}_{\mathbb{C}}^n$ and $Y = \mathbb{A}_{\mathbb{C}}^n \times \mathbb{A}_{\mathbb{C}}^1$, here $\mathbb{A}^{1}_{\mathbb{C}}$ is with coordinate $t$.
    For $f \in \mathbb{C}[x_1, \cdots, x_n]$, Consider $M = \mathbb{C}[x_1, \cdots, x_n]_f[s] f^s$.

    Define $t M = f M$ and then $t^{-1} M = f^{-1} M$.  Take $s = -t\partial_t$, then $\partial_t = -t^{-1} s$, the $\partial_{t}$-action is defined, and further, $M$ is a $\mathcal{D}_Y = \mathcal{D}_X \langle t, \partial_t \rangle$-module.

    Then $N := \mathbb{C}[x_1, \cdots, x_n][\partial_t] f^s = \mathbb{C}[x_1, \cdots, x_n][\partial_t] f^s= \mathbb{C}[x_1, \cdots, x_n][t^{-1} s] f^s$, and $\partial_{x_i} f^s = \partial_{x_i}(f) \cdot \frac{1}{f} s f^s= \partial_{x_i}(f) \cdot (-\partial_t) f^s$, thus $N$ is a $\mathcal{D}_Y$-submodule of $M$. Furthermore, we can check that $\mathrm{Ch}(N)$ = the conormal bundle of the graph of $X$, which indicates that $N$ is a holonomic $\mathcal{D}_{Y}$-module.

    We consider $V_{i}\mathcal{D}_{Y}\cdot f^{s}$ forming a good filtration of $N$: $$V_0 \mathcal{D}_Y \cdot f^s = \mathcal{D}_X \langle t, s \rangle f^s = \mathcal{D}_X[s] f^s$$Similarly, $V_{-1} \mathcal{D}_Y \cdot f^s = \mathcal{D}_X[s] f^{s+1}$.

    By Theorem \ref{Theorem 8.4}, there exists $b(s) \in \mathbb{C}[s]$ s.t.$$
        b(s) \cdot \frac{V_0 \mathcal{D}_Y \cdot f^s}{V_{-1} \mathcal{D}_Y \cdot f^s} = b(s) \cdot \frac{\mathcal{D}_X[s] f^s}{\mathcal{D}_X[s] f^{s+1}} = 0.$$which is to say there exists $P(s)\in \mathcal{D}_{X}[s]$ such that $b(s) f^s = P(s) \cdot f^{s+1}$

    In fact, $N = \iota_{f,+} (\mathbb{C}[x_1, \ldots, x_n])$, the $\mathcal{D}$-module pushforward, where $$\iota_f: X \to Y = X \times \mathbb{A}^{1}_{\mathbb{C}}\atop x \mapsto (x, f(x))$$the graph embedding. So $N$ is regular holonomic, and $b(s) \neq 1$.
\end{example}

\begin{remark}
    One can replace $\mathbb{C}[x_1, \ldots, x_n]$ by any regular holonomic $\mathcal{D}_X$-module, to get similar results in general.
\end{remark}
