\documentclass[12pt]{article}
\usepackage[letterpaper,margin=1.01in]{geometry}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{mathrsfs}
\usepackage{microtype}

\title{Homework: week 2}
\date{October 7, 2025}

\begin{document}
\maketitle

\bigskip
$A$: a ring with unit (possibly not commutative) with a $\mathbb{Z}_{\ge 0}$-filtration $\Gamma_\bullet A$.

$X=\operatorname{Spec}R$: a smooth affine algebraic variety over $\mathbb{C}$ of finite type

\bigskip
\noindent
\textbf{Problem 1.} Let $M$ be a finitely generated $D_X$-module. Prove that if $F_\bullet M$ is a good
filtration, then $F_p M$ is a finitely generated $R$-module for every $p$.

\bigskip
\noindent
Hint: prove $F_p D_X$ finitely generated over $R$ first.

\bigskip
\noindent
\textbf{Problem 2.} Let $M$ be a $D_X$-module with a compatible filtration $\Omega_\bullet M$ such that $\Omega_p M$ is
finite generated over $R$ for every $p$. Then $\Omega_\bullet M$ is called a ``good'' filtration if there exists
$n_0 \gg 0$ such that
\[
F_j D_X\cdot \Omega_i M = \Omega_{i+j} M \quad \forall j \ge 0,\, i \ge n_0.
\]
Prove that $\Omega_\bullet M$ is ``good'' iff $\operatorname{gr}^\Omega_\bullet M$ is finitely generated over $\operatorname{gr}^F_\bullet D_X$,
i.e. ``good'' filtrations $\Longleftrightarrow$ good filtrations we defined previously.

\bigskip
\noindent
\textbf{Problem 3.} For $x \in X$ a closed point, we use $m_x$ to denote its maximal ideal. Prove that
we have canonical isomorphisms
\[
(m_x/m_x^2)^* := \operatorname{Hom}(m_x/m_x^2,\mathbb{C}) \simeq T_{X,x} := T_X \otimes_R R/m.
\]
and
\[
 m_x/m_x^2 \simeq \Omega_{X,x} := \Omega_X \otimes_R R/m.
\]

\bigskip
\noindent
Hint: use the natural map $d:R\to \Omega_X$ to induce a map $(m_x/m_x^2)^* \to T_{X,x} = \operatorname{Hom}_R(\Omega_X,R/m_x);$
then prove both of them are surjective.

\noindent
$(m_x/m_x^2)^*$ is called the \emph{zariski tangent space} of $X$ at $x$.

\bigskip
\noindent
\textbf{Problem 4.} Use problem 3 to prove that if $m \subset R$ is a maximal ideal, then we can find
$x_1,\ldots,x_n \in m$ such that $m = (x_1,\ldots,x_n)$ and $(x_1,\ldots,x_n)$ is an algebraic coordinate system
on $X$.

\bigskip
\noindent
Hint: use Nakayama's Lemma.

Assume that $\Gamma_\bullet A$ is a almost commutative ring, i.e. $\operatorname{gr}^\Gamma_\bullet A$ is a commutative ring. For
$x \in \Gamma_k A$, $\sigma_k(x)$ is the image $x$ in $\Gamma_k A/\Gamma_{k-1}A$. For $x \in \Gamma_k A$, $y \in \Gamma_l A$, since $\operatorname{gr}_\bullet A$ is commutative,
we define
\[
\{\sigma_k(x),\sigma_l(y)\} = \sigma_{k+l-1}(xy - yx).
\]

\bigskip
\noindent
\textbf{Problem 5.} Prove that $(\operatorname{gr}_\bullet A,\{\cdot,\cdot\})$ is a well-defined Poisson algebra.

\bigskip
Meanwhile, we have its Rees ring $R_\bullet(A) = \bigoplus_i \Gamma_i A\cdot u^i$. Define $T := \frac{R_\bullet(A)}{u^2\cdot R_\bullet(A)}$.

\bigskip
\noindent
\textbf{Problem 6.} Prove that $T/u\cdot T \xrightarrow{u} u\cdot T$ is an isomorphism.

\bigskip
\noindent
We have another Poisson bracket on $\overline{T} = T/u\cdot T \simeq \operatorname{gr}^\Gamma_\bullet A$ defined by for $a,b\in T$
\[
\{\overline{a},\overline{b}\} = \overline{c}
\]
such that $\overline{c} \in \overline{T}$ is given by $ab - ba \in u\cdot T$ by using the isomorphism in Problem 6.

\bigskip
\noindent
\textbf{Problem 7.} Prove that the above two Poisson structure on $\operatorname{gr}_\bullet A$ are the same.

\bigskip
\noindent
\textbf{Problem 8.} If $M$ is an integrable connection on $X$, then prove that $Ch(M)=T_X^*X$.

\bigskip
\noindent
Hint: First, prove that there exists a finite open covering $X=\bigcup_i U_i$ with $U_i=\operatorname{Spec}R_{f_i}$ for
some $f_i \in R$ such that $M_{f_i}$ is free over $R_{f_i}$.
\end{document}
